\documentclass[oneside, 12pt]{memoir}
\usepackage{verbatim}
\usepackage[labelsep=period, font=singlespacing, skip=12pt, format=hang, justification=RaggedRight, singlelinecheck=false]{caption}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{indentfirst}
\usepackage{thesis}
\usepackage{frontmattercontents}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{layouts}

\graphicspath{{./images/}}

\lstset{ %
xleftmargin=.2in,
xrightmargin=.1in,
language=Python,                	% choose the language of the code
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=2,                   % the step between two line-numbers. If it's 1 each line 
                                % will be numbered                                                         
numbersep=5pt,                  % how far the line-numbers are from the code
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=single,	                % adds a frame around the code
tabsize=2,	                	% sets default tabsize to 2 spaces
captionpos=b,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
title=\lstname,                 % show the filename of files included with \lstinputlisting;
                                % also try caption instead of title
escapeinside={\%*}{*)},         % if you want to add a comment within your code
morekeywords={*,...}            % if you want to add more keywords to the set
}


\checkandfixthelayout
\begin{document} 
	\setdoctype{Polemic}
	\masters 
	
	
\settitle{Modeling Mobile Web Characteristics for Energy Optimized Delivery}
\setauthor{Troy Johnson}

\setdefdate{September 2014}
\setgraddate{December, 2015}

\setchair{Dr. Patrick Seeling, Ph.D.}
\setmembers{Dr. Patrick Kinnicutt, Ph.D. \\ Dr. Michael Stinson, Ph.D.}


\newcommand{\titlepage}{{
\clearpage
\thispagestyle{empty}

\begin{SingleSpace}
\centering
\cmutitle \\
\vspace{1.42in} 
\cmuauthor \\
\vspace{1.42in}
A thesis submitted in partial fulfillment of\\
the requirements for the degree of\\
Master of Science \\
\vspace{2.333in}
Department of Computer Science \\
\vspace{2in}
Central Michigan University\\
Mount Pleasant, Michigan \\
September 2014\\
\end{SingleSpace}
\clearpage}}


\newcommand{\signaturepage}{{
\clearpage
\thispagestyle{plain}
{\centering
Accepted by the Faculty of the College of Graduate Studies,\\
Central Michigan University, in partial fulfillment of\\
the requirements for the master's degree\\}
\vspace{12pt}
{\noindent
Thesis Committee:\\}
\setlength{\tabcolsep}{0mm}
\begin{tabular}{{@{}l @{\hspace{10mm}}l}}
\rule{92mm}{.3pt}  &  Dr. Patrick Seeling \\
\rule{92mm}{.3pt}  &  Dr. Patrick Kinnicutt \\
\rule{92mm}{.3pt}  &  Dr. Michael Stinson \\
Date: \rule{81mm}{.3pt} & \\
\rule{92mm}{.3pt}  &  Dean \\ 
Date: \rule{81mm}{.3pt} & \parbox[tl]{2in}{\vspace*{-32pt} College of Graduate Studies} \\
\end{tabular}\\

{\noindent
Committee:\\
 
}
\clearpage}}

\newcommand{\acknowledgementspage}{{%
\clearpage
\thispagestyle{plain}

{\centering
ACKNOWLEDGMENTS \\}
This work was sponsored by an Early Career Grant from the Office of Research and Sponsored Programs at Central Michigan University. I wish thanks to A. Sampson and R. Kohvakka for assistance in the development of the testbed measurement environment.
%\end{Spacing}
\clearpage}}


\newcommand{\abstractpage}{{
\clearpage
\thispagestyle{plain}

{\centering
ABSTRACT \\
\begin{SingleSpace}
\cmutitle \end{SingleSpace}
by Troy Johnson\\}

As mobile traffic and data consumption continue to rise, there is a growing need to investigate increased energy efficiency and optimizations to reduce the bandwidth when browsing the mobile web. Use cisco figure citations here???? To determine the reduction in energy consumption of mobile devices, there is also a need for a way to measure the energy consumption of mobile devices. By investigating the composition and characteristics of mobile web pages, statistical models can be derived for describing the characteristics of a typical mobile web page, such as the individual response sizes and expiration ages of responses that mobile browsers request for web pages.HTTP Archive will be a great source of data that may be utilized to derive models for describing the mobile web. Additionally, this pool of data is updated on a bimonthly basis, providing a constantly updated pool of data to update the developed models with and validate them. These models can then in turn be used to provide more accurate results when estimating the possible energy and bandwidth savings by using these models for generating artificial web pages that will contain characteristics that closely resemble those characteristics often found on the actual mobile web.  Investigating the models and data further, they can be extended to create prediction models that will describe the growing mobile web for future years. With these models in place, they can be applied to projects for optimizing energy and bandwidth consumption on mobile devices, such as the possible energy and bandwidth savings that can result from cache forwarding between desktop computers and mobile devices. To measure the possible energy consumption savings from these projects, a low cost test bed for measuring the power consumption of mobile devices can be employed as a baseline
\clearpage}}

	

\frontmatter
\setulmarginsandblock{0.75in}{1.25in}{*}
\titlepage
\clearpage
\pagebreak
\begin{Spacing}{2}
\acknowledgementspage
\clearpage
\pagebreak
\abstractpage
\clearpage
\pagebreak
\tableofcontents*
\clearpage
\pagebreak
\listoffigures
\clearpage
\pagebreak
\pagestyle{plain}
\checkandfixthelayout
\mainmatter
\counterwithout{figure}{chapter}
\addtocontents{toc}{\noindent CHAPTER \par}
\setulmarginsandblock{0.75in}{1.25in}{*} 



\input{content/Chapter1_Intro}
\input{content/Chapter2_Testbed}
\input{content/Chapter3_ProxyServer}
\input{content/Chapter4_CacheForwarding}
\input{content/conclusion}

\end{Spacing}
\bibliographystyle{unsrt}
\bibliography{main}
\end{document}
