 \chapter{INTRODUCTION}
\label{ch:introduction}
The increased ubiquity of mobile devices has accelerated the growth of mobile data usage tremendously. Cisco, Inc. predicts that the total monthly global mobile data traffic will exceed 15 exabytes by 2018 \cite{VNI14}. With this increase in traffic also comes the increased need for optimizations on how content is delivered to mobile devices. Optimizations for mobile devices can help reduce the load being put on mobile networks through more effective caching or pre-caching, optimizing the delivery of content to mobile devices, and many other ways. To determine the potential achievable savings of these optimizations, simulations can be performed which simulate a typical user session when browsing the mobile web over an extended period of time. These simulations can use data from an actual pool of mobile web pages, or statistical models that have been developed which describe the characteristics of a typical mobile web page. HTTP Archive \cite{ht13} is one such tool that provides pools of data about the characteristics of the most popular desktop and mobile web pages. Statistical models have the advantage of being able to be extended to show what we expect web pages to look like in the future and don't require the storage overhead for having a pool of data containing all the characteristics of the most popular web pages.

\section*{HTTP Archive}
\addcontentsline{toc}{section}{HTTP Archive}
The data contained in HTTP Archive is mined and utilized for several of the projects in the following chapters. HTTP Archive is an online repository of web performance information containing information on both desktop and mobile versions of websites. Information gathered includes all the details about the responses web pages make such as the size and expiration age. An exhaustive list of the characteristics gathered by HTTP Archive can be found on their website (http://httparchive.org). The information gathered only pertains to the characteristics of the landing page of the web site. HTTP Archive gathers their data using a private instance of WebPageTest (http://www.webpagetest.org). According to HTTP Archive, the determination of which web pages are to be archived is based on set derived from the union of the following sets of sources: Alexa 500, Alexa US 500, Alexa 10,000, Fortune 500, Global 500, and Quantcast10K.